### 2014-01-27 brains-protocol.tex
Flesh out classical measures, add an open question to be solved

@@

\RK{introduce the classical psycholinguistic measures -- kind of like ``demographic'' usual suspects}

We also considered grammatical types within quotations by detection of \emph{Part-of-Speech} (POS) categories, using the Penn TreeBank Project typology \citep{Santorini90} and thereby distinguishing verbs, nouns, adjectives and 
adverbs.  The results were however extremely similar across the various categories, exhibiting no specific behavior of words belonging to different POS categories. %. \tb{Enfin, on ajoute à ces mesures la catégorie grammaticale, dans les citations, des mots échangés lors des substitutions. On s'est restreint à quatre des catégories les plus fréquentes, en utilisant la catégorisation et la notation des \emph{Part-of-Speech} (abrégé POS)\footnote{Le terme \emph{Part-of-Speech}, ou "partie du discours" en français, désigne les catégories grammaticales des mots (ou même des parties de mots) utilisées en linguistique.} du Penn TreeBank Project\footnote{Le Penn TreeBank Project définit une typologie très complète des POS, ainsi qu'une façon de les noter : à chaque POS correspond un code de deux ou trois lettres majuscules. Par exemple, tous les POS tenant du verbe commencent par la lettre $V$ (e.g. $VBN$ pour participe passé, $VBG$ pour participe présent, etc.).}~\citep{Santorini90} : verbes (POS dont le code commence par $V$), noms (POS dont le code commence par $N$), adjectifs (POS dont le code commence par $J$), et adverbes (POS dont le code commence par $R$). Cette mesure supplémentaire affine les observables définies ci-dessus, et permet d'observer un éventuel effet des catégories grammaticales sur les résultats.}

\subsubsection{Network-based definitions}
We rely on two types of network-based data: curated synonym associations provided by WordNet~\citep{WordNet10}, and ``free association'' relationships collected by~\citet{Nelson04}.

>>>>

To keep the analysis palatable, we restricted the analysis to quotation transformations which consisted in the \emph{substitution} of a word by another word (and only those cases).
To quantify those substitutions, we decided to associate a number of features to each word, the variation of which we can statistically study.
The following sections detail the features we used.

@@

We first introduced some of the most classical psycholinguistic measures on words:

\begin{itemize}
    \item \textbf{Age of Acquisition}: the average age at which words are learned, obtained from~\citet{kuperman12},
    \item The average \textbf{Number of Phonemes} for all pronunciations of a word, obtained from the Carnegie Mellon University Pronouncing Dictionary~\citep{Weide98},\footnote{The CMU Pronouncing Dictionary is included in the NTLK package~\citep{Bird09}, the natural language processing toolkit we used for the analysis.}
    \item The average \textbf{Number of Syllables} for all pronunciations of a word, also obtained from the CMU Pronouncing Dictionary.
    \item \rk{Why exactly don't we include word frequencies as a measure?}
\end{itemize}

We also considered grammatical types within quotations by detection of \emph{Part-of-Speech} (POS) categories, using the Penn TreeBank Project typology~\citep{Santorini90} and thereby distinguishing verbs, nouns, adjectives and adverbs.
The results were however extremely similar across the various categories, exhibiting no specific effect of words belonging to different POS categories.

\subsubsection{Network-based definitions}

We rely on two types of network-based data: curated synonym associations provided by WordNet~\citep{WordNet10}, and ``free association'' relationships collected by~\citet{Nelson04}.
